Decoupled Fallback: A Portable Single-Pass GPU Scan

### 2025-02-05 paper.tex
Update Appendix to include Dawn (again)

\subsection{Availability}
We provide our artifact in the following GitHub repository:
\thomas{Will anonymize with GithubAnonymous once we are ready.}.

@@

>>>>

@@

\subsection{Availability}
We provide our artifact in the following GitHub repository: 
\thomas{Will anonymize with GithubAnonymous once we are ready.} 
We provide both Dawn and WGPU implementations for testing. However, we recommend Dawn, and only use WGPU for ease of native testing on Android.

\subsection{Requirements}

\subsubsection{Device Requirements}
Any device supporting Dawn, with subgroup and timestamp query capabilities, and at least 384 MB of available device memory.

\subsubsection{Software Requirements}
\begin{itemize}
  \item Git
  \item CMake 3.10.2+ or another C++ build tool
  \item C++17-compliant compiler
  \item Python for fetching dependencies
\end{itemize}

\subsection{Building}
Although native WebGPU is supported on various operating systems—most notably Windows, macOS, and Linux—this section will focus on building it in Unix-like environments for the sake of brevity, using CMake as the example build tool.

\subsubsection{Building Dawn}
\begin{enumerate}
  \item[(0)] Dawn depends on the following packages (Ubuntu package names):
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
sudo apt install libxrandr-dev \
  libxinerama-dev libxcursor-dev libxi-dev \
  libx11-xcb-dev mesa-common-dev
  \end{lstlisting}

  \item Clone the Dawn repository:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
git clone https://dawn.googlesource.com/dawn
cd dawn
git fetch --all
git checkout chromium/6950
  \end{lstlisting}

  \item Build and install Dawn with your build tool and compiler of choice:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cd dawn
cmake -S . -B out/Release \
  -DDAWN_FETCH_DEPENDENCIES=ON \
  -DDAWN_ENABLE_INSTALL=ON \
  -DCMAKE_BUILD_TYPE=Release \
  -DDAWN_BUILD_TESTS=OFF \
  -DDAWN_BUILD_SAMPLES=OFF \
  -DTINT_BUILD_TESTS=OFF \
  -DTINT_BUILD_CMD_TOOLS=OFF

cmake --build out/Release \
  --parallel <num_threads>

cmake --install out/Release \
  --prefix install/Release
  \end{lstlisting}
\end{enumerate}

\subsubsection{Building Artifact}
After successfully building and installing Dawn, follow these steps to build the artifact:

\begin{enumerate}
  \item Navigate to the artifact directory:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cd Decoupled-Fallback-Paper/artifact/Dawn
  \end{lstlisting}

  \item Set the `CMAKE\_PREFIX\_PATH` to point to your Dawn installation directory:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
export CMAKE_PREFIX_PATH=/path/to/dawn/ \  
  install/Release
  \end{lstlisting}

  \item Build the artifact:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cmake -S . -B out/Release \
  -DCMAKE_BUILD_TYPE=Release
  \end{lstlisting}

  \item Compile the project:
  \begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
cmake --build out/Release
  \end{lstlisting}
\end{enumerate}

\subsubsection{Running the Artifact}
Once the artifact has been successfully built, you can run it using the following command:

\begin{lstlisting}[basicstyle=\ttfamily\small, frame=single]
./out/Release/dawn <TestType> [record] [deviceName]
\end{lstlisting}

where:
\begin{itemize}
    \item \texttt{<TestType>} specifies the test to run. Valid options are:
    \begin{itemize}
        \item \texttt{csdl} – Runs the \emph{Decoupled Lookback} test. \textbf{Warning}, this \emph{will} crash without FPG. 
        \item \texttt{csdldf} – Runs the \emph{Decoupled Fallback} test.
        \item \texttt{full} – Runs a full set of tests, including multiple \emph{Decoupled Fallback} simulations.
    \end{itemize}
    \item \texttt{record} (optional) enables recording the test results to a CSV file.
    \item \texttt{deviceName} (optional) appends the device name to recorded test results.
\end{itemize}
